\thesistitle

### 2019-08-17 sections/results.tex
Put in the new graphs

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{img/duplication}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
  \label{fig:duplication}
\end{figure*}

>>>>

\subsection{Type 2R Variability Threshold}
To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expression). Figure \ref{fig:t2rgraph} shows the results.

\begin{figure}
  \includegraphics[width=1\textwidth]{img/T2R}
  \caption{Cloned nodes found for different Type 2R thresholds.}
  \label{fig:t2rgraph}
\end{figure}

\subsection{Type 3R Gap Size Thresholds}
To determine the influence of the type 3R gap size threshold on the amount of found nodes, we ran CloneRefactor for all gap size percentages between 0\% and 200\%. Figure \ref{fig:t3rgraph} shows the results.

\begin{figure}
  \includegraphics[width=1\textwidth]{img/T3R}
  \caption{Cloned nodes and clone classes found for different Type 3R thresholds.}
  \label{fig:t3rgraph}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=1\textwidth]{img/duplication}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
  \label{fig:duplication}
\end{figure}
